%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Industry}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Partner} % Role
    {Now \& Net} % Event
    {Paris, France} % Location
    {2013 - 2015} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Member of a startup, created in 2012, aiming at providing a collective musical experience organised around DJ-ing.}
        \item {Writing of research and development plans leading to the successful application to the status of young innovative company (JEI). Development of a proof-of-concept recom- mender system based on the technology Neo4j.}
      \end{cvitems}
    }

  \cventry
    {Multiple Positions} % Role
    {Ericsson AB} % Event
    {Stockholm, Sweden} % Location
    {2008 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {SCRUM master and Software Developer - 2013/2014: Acting as the “guardian of the process“ to facilitate daily operations of a cross functional team (8 people). Animation of planning meetings, daily follow-up meetings and retrospective meetings.}
        \item {System engineer at AT\&T laboratory - summer 2012: Integration of features into the customer network with laboratory and in-the-field experiments.}
        \item {Research engineer at Ericsson Research - 2012: Preparation of the 4G+ prototype for the Mobile World Congress (MWC).}
        \item {Software Developer at 4G/LTE - 2008/2011: Development in C of algorithms from standard specifications (3GPP). Extension and support of an Erlang test framework used by 50 engineers, including training sessions in Stockholm and Beijing.}
        % \item {reference: Mathias Ekwing - mathias.ekwing@ericsson.com}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
