%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Post-doctoral Researcher} % Job title
    {Inria} % Organization
    {Saclay, France} % Location
    {Jan. 2020 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the team Ex)Situ which explores the limits of human-computer interaction, specifically how extreme users interact with technology in extreme situations.}
        \item {Research with Dr. Caramiaux on problems related to the measure of motor learning in tasks involving complex and creative motions, such as dance or music practise.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research and Teaching Assessment Assistant} % Job title
    {University of Glasgow} % Organization
    {Glasgow, United Kingdom} % Location
    {Mar. 2019 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research with Pr. Chalmers on visualisation techniques for low-dimensional embeddings with a focus on bridging t-SNE and force-based approaches. Production of Jupyter notebooks gathering the Python implementation of proposed algorithms and results of experiments on Mnist-Fashion.}
        \item {Assessment of undergraduate projects and tutoring courses. Correction of examination essays.}
        % \item {reference: Pr. Chalmers - matthew.chalmers@glasgow.ac.uk}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PhD Candidate and Contributor to the European Project MoreGrasp} % Job title
    {University of Glasgow} % Organization
    {Glasgow, United Kingdom} % Location
    {Mar. 2015 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the Inference, Dynamics and Interaction (IDI) group led by Pr. Murray-Smith.}
        \item {Research involving computational methods for the study of novel gestural interactions: use of discriminative models to create virtual surfaces from RGB-D sensors, optimisation of gameplay experiences for custom game controllers via user probabilistic modelling, audio-based reinforcement learning for the exploration and characterisation of user physical capabilities. Partly published at ISS’17.}
        \item {Contributions to the European project MoreGrasp: lead redaction of deliverable documents, implementation of visual feedback mechanisms on smartwatches, preparation of live demos and posters for review meetings, establishment of contacts with practitioners in the QEU hospital in Glasgow leading to workshops in-situ and the writing of a funding proposal targeting a local charity.}
        \item {Tutoring for Artificial Intelligence and Data Fundamentals courses (undergraduate, Master levels).}
        % \item {references: Pr. Murray-Smith - rod@glasgow.ac.uk, Dr. Williamson - jhw@glasgow.ac.uk}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Mobile Vinn Excellence Center (Mobile Life)} % Organization
    {Stockholm, Sweden} % Location
    {Feb. 2014 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of Pr. Brown’s group dedicated to the understanding of human interactions with novel technology through the use of ethnographic methods.}
        \item {Research on innovative designs for always-on in the background speech interactions. Design of an experiment involving day-long recordings of participants’ everyday life. Qualitative analysis and design workshop with trained Interaction designers. Published at CHI’15.}
        % \item {reference: Pr. Brown - barry@dsv.su.se}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
